### 2021-11-24 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@e2a0b519d1b2c9d8359dc223295000db86aacddb 🚀

We begin by proposing a method to compute a null expectation of the
probability of an interaction false-negative as a function number of
total observations of individuals of \emph{all species in the species
pool}. This is done by simulating the process of observation, where the
probability of observing a given species is its relative abundance. We
use a log-normal distribution of relative abundance (Hubbell 2001) and
simulating the process of observation on food-webs generated using the
niche model (Williams \& Martinez 2000) with connectance parameterized
by the flexible-links model (MacDonald \emph{et al.} 2020). An example
of this relation for networks with varying spceies richness is shown in
fig.~\ref{fig:fnr}.

@@

\begin{figure}
\hypertarget{fig:fnr}{%
\centering
\includegraphics{./figures/ch2_fnr.png}
\caption{foo}\label{fig:fnr}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:posassoc}{%
\centering
\includegraphics{./figures/positiveassociations.png}
\caption{Demonstrates positive associations in
co-occurrence}\label{fig:posassoc}
}
\end{figure}

@@

\textbf{TK} By using the success of numerical-weather prediction and the
Earth monitoring system that supports it as a model,

>>>>

We begin by proposing a method to compute a null expectation of the
probability of an interaction false-negative as a function number of
total observations of individuals of \emph{all species in the species
pool}. This is done by simulating the process of observation, where the
probability of observing a given species is its relative abundance. We
show that the realized false-negative rate can be quite high, simply as
a byproduct of the distributoin of relative abundance in communities. We
use a log-normal distribution of relative abundance (Hubbell 2001) and
simulating the process of observation on food-webs generated using the
niche model (Williams \& Martinez 2000) with connectance parameterized
by the flexible-links model (MacDonald \emph{et al.} 2020). An example
of this relation for networks with varying spceies richness is shown in
fig.~\ref{fig:fnr}.

\begin{figure}
\centering
\includegraphics{./figures/negativebinomial.png}
\caption{Relationship between total number of observed interactions
negatives (x-axis) and the probability that an interaction is a
true-negative as a function of different realized false-negative rates
(colors), assuming each observed negative is independent---the same as
the negative-bernoulli distribution.}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:fnr}{%
\centering
\includegraphics{./figures/ch2_fnr.png}
\caption{The realized false-negative-rate of interaction detection
(y-axis) as a function of the total number of observations of all
species in the species pool (different richnesses in different colors).
Each point is the mean of 50 replicates, with one standard-deviation in
the first shade, and two standard deviations in the second
shade.}\label{fig:fnr}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:posassoc}{%
\centering
\includegraphics{./figures/positiveassociations.png}
\caption{Demonstrates positive associations in co-occurrence. Left: the
product of the marginal probability of observing two species (A and B)
in a sample (x-axis) agaianst the computed joint probability of
observing these species together (y-axis). Dashed line indicates
\(y=x\), meaning no association between the two. Each point is an
observed interaction between two species. Right: the distribution of the
difference between these joint and marginal probabilities. Both are
non-zero with \(p < 10^-50\) via a t-test.}\label{fig:posassoc}
}
\end{figure}

@@

Biodiversity science would be wise to use the success of
numerical-weather prediction and the Earth monitoring system that
supports it as a template. Further, we should embrace methodological
advances in computational statistics that can enable more robust
prediction of the dynamics of complex systems than is possible using the
tools of analytic models---not just because they can provide more
efficacious predictions, but also because they enable a more direct
representation of uncertainty, which is crucial for developing
ecological forecasting models which provide actionable information to
stakeholders.
